\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/sections/patterns_in_wrong_questions.tex
Update src/tex/sections/patterns_in_wrong_questions.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\glspl{llm} also struggle with questions that do are not \glspl{mcq}.
Albeit in our study, we only investigated numerical outputs that can be parsed and scored. Thus, a part of these would involve multi-step calculations, which can be challenging for \glspl{llm}.\autocite{zhou2023llm_arithmetics}

>>>>

\glspl{llm} also struggles with questions that require numerical outputs. Some of these involve multi-step calculations, which can be challenging for \glspl{llm}.\autocite{zhou2023llm_arithmetics}
